\chapter*{Acknowledgments}% (fold)
\label{sec:woord-vooraf}
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Acknowledgments}

First of all I would like to thank Showpad as a whole and especially vice president engineering Chris De Mol for allowing me to do my internship in such an interesting company.

I would also like to thank everyone in the engineering team for helping me get up to speed with all of the Showpad engineering projects. In particular I would like to acknowledge Mike Warner, my team coach, for explaining me the high-level architecture of the Showpad platform and for including me in all important team activities.

Another person I would like to thank personally is Laurens Dewaele, my internship supervisor. I would like to thank Laurens for taking the time to explain the web app v2 architecture to me in detail. He really enabled me to do all the work I did on the project during my internship. The occasional pair programming sessions we did together helped me gain a deeper understanding of functional reactive programming.

I am also especially thankful to Mike, Laurens and everyone else in the share \& personalize team for always taking the time to answer my questions and for listening to my input. A special thanks also goes out to Thibaut Nguyen, Arnaud Schlupp, Stijn Deschuymer and everyone else involved with web app v2 for integrating me into the project and helping me in general.

My academic supervisor Rogier van der Linde also deserves a word of thanks for his great guidance and advice during the writing of this bachelor thesis. I also want to acknowledge him, Laurens Dewaele, Arnaud Weyts and everyone else that took the time to review this bachelor thesis and give feedback.

Finally I am sincerely grateful to my family and my girlfriend for their continuous support during the busy period writing this bachelor thesis and doing my internship.